\tool: Revisiting BadUSB with Type-C

### 2021-03-04 WOOT/Files/badusb.tex
nits
impl free of GoodUSB

We also assume the victim's device is equipped with fully functional USB 3.x
protocol and USB Type-C connector. As the USB 3.x standard is
common nowadays, this assumption can be easily fulfilled especially in recent
devices.

@@

%Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber,
%rubberducky2020} emulates as a HID device enabling various arbitrary execution
%attacks, fetching feedback from the victim is much more limited.
Based on the drawbacks introduced above, several defense mechanisms were
proposed. GoodUSB~\cite{tian2015defending}
implemented a CAPTCHA-like~\cite{captcha} procedure, which requires user to
complete certain challenges when an unknown HID device is plugged in. As the
BadUSB is only able to emulate a limited kind of devices such as HIDs or disks, by
no means the BadUSB can bypass it.

In this work, we utilize the new features of USB 3.x~\cite{usb31,usb32} to
address the problem above.  Benefiting from the latest protocol, we simulate
external display and thus obtain the video stream to perform accurate
attacks.
Thus, our \tool is capable of
bypassing defenses such as GoodUSB. Taking advantage of USB 3.x~\cite{usb31,usb32},
\tool can fetch the video stream of the victim and complete the challenge
manually by the attacker. Moreover, with video capability combined with
traditional BadUSB, our \tool achieved multiple new attack paradigms and are
tested under various real-world scenarios.

@@

	\caption{Attack Model}%\shuqing{Need to be more compact.}
	\label{fig:attack_model}
\end{figure}

@@

First, \tool supports defense-bypassing. As the original BadUSB cannot get
feedback from the victim, defense mechanisms like GoodUSB~\cite{tian2015defending} are sufficient to prevent these BadUSB attacks.
However, these defense mechanisms leverage visual notification to block access
for unknown USB devices. This means that when the defense requests authorization
from the user, our \tool is able to capture the content of authorization
challenge and bypass it. After the defense is bypassed, \tool continues the
emulation and script execution, resulting in a successful attack.

@@

The advantage of this mode is that it archives defense bypass and attack
feedback with video streaming.  
%\fengwei{I don't understand the sentence below.}\hongyi{Fixed, I think it's redundant and less important}
%As mentioned above, we only require video stream at the beginning (defense
%bypass) and the end (result feedback) of the attack.
Moreover, with mouse
supported, \tool extends the original BadUSB attack and results in further attacks in
mobile devices.

>>>>

We also assume the victim's device is equipped with fully functional USB 3.x
protocol and USB Type-C connector. As the USB 3.x standard is
common nowadays, this assumption can be fulfilled in recent
devices.

@@

%Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber,
%rubberducky2020} emulates as a HID device enabling various arbitrary execution
%attacks, fetching feedback from the victim is much more limited.
Based on the drawbacks introduced above, several defense mechanisms were
proposed. For example, GoodUSB~\cite{tian2015defending}
implemented a authorization procedure when a new device is plugged in and blocks other functions excepted authorized ones.

In this work, we utilize the new features of USB 3.x~\cite{usb31,usb32} to
address the problem above.  Benefiting from the latest protocol, we simulate
external display and thus obtain the video stream to perform accurate
attacks. However, we still unable to bypass defenses like GoodUSB~\cite{tian2015defending}, which completely blocks unauthorized functionality. This will be further discussed in Section~\ref{sec:discussion}

@@

	\caption{Attack Model.}%\shuqing{Need to be more compact.}
	\label{fig:attack_model}
\end{figure}

@@

First, as \tool has established a feedback channel using USB 3.2 protocol, when performing keystroke and mouse movement injection, attacker can obtain real-time feedback from the victim's devices. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such feedback channel largely strengthen the attack ability of \tool.

@@

The advantage of this mode is that it archives defense bypass and attack
feedback with video streaming.  
%\fengwei{I don't understand the sentence below.}\hongyi{Fixed, I think it's redundant and less important}
%As mentioned above, we only require video stream at the beginning (defense
%bypass) and the end (result feedback) of the attack.
Also, with mouse
supported, \tool extends the original BadUSB attack and results in further attacks in
mobile devices.

### 2021-03-04 WOOT/Files/introduction.tex
impl free of GoodUSB

In this work, we proposed our approach addressing the limitations mentioned
above and implemented a multi-mode attack model of USB, named \tool.  \tool
extends BadUSB to support the features of USB Type-C.  Since USB Type-C is
capable to transfer video stream data, \tool could obtain the information of
victim's graphical interface during attacks.  Combining it with the emulation
of traditional HIDs like keyboards and mice, attackers are capable of
performing precise attacks.  We did experiments to verify that \tool could also
bypass many countermeasures for BadUSB since they often rely on interaction
with the graphical interface.  Moreover, we implemented multiple attacking
modes of USB attacks based on our approach to verify its effectiveness,
including HID Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the USB devices they
plugged in for security purposes.  
10 volunteers are involved in the user study.
At last, we found that 4,796 of 94,058 records obtained by \tool are related to privacy information of users.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated UI rendering, to separate the user interface
into sensitive and insensitive layers.  Only content on the insensitive layer
will be passed to the insecure driver and thus rendered on the external
display, which protects content on the sensitive layer.
%\shuqing{Case study, evaluation, notable results.}

@@

    \item Our approach can bypass many previous countermeasures of BadUSB.

>>>>

In this work, we proposed our approach addressing the limitations mentioned
above and implemented a multi-mode attack model of USB, named \tool.  \tool
extends BadUSB to support the features of USB Type-C.  Since USB Type-C is
capable to transfer video stream data, \tool could obtain the information of
victim's graphical interface during attacks.  Combining it with the emulation
of traditional HIDs like keyboards and mice, attackers are capable of
performing precise attacks.  We did experiments to verify that \tool could also
bypass some countermeasures for BadUSB since they often rely on interaction
with the graphical interface.  Moreover, we implemented multiple attacking
modes of USB attacks based on our approach to verify its effectiveness,
including HID Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the USB devices they
plugged in for security purposes.  
10 volunteers are involved in the user study.
At last, we found that 4,796 of 94,058 records obtained by \tool are related to privacy information of users.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated UI rendering, to separate the user interface
into sensitive and insensitive layers.  Only content on the insensitive layer
will be passed to the insecure driver and thus rendered on the external
display, which protects content on the sensitive layer.
%\shuqing{Case study, evaluation, notable results.}

@@

    %\item Our approach can bypass some previous countermeasures of BadUSB.
